\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage[english]{babel}
\usepackage[margin=1cm, top=1cm, bottom=1cm]{geometry}
\usepackage{paracol}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{titlesec}
\usepackage{setspace}
\usepackage{lmodern}
\pagestyle{empty}

% --- Colors ---
\definecolor{darkblue}{RGB}{0, 0, 139}
\definecolor{graytext}{RGB}{80, 80, 80}

% --- Font ---
\usepackage[sfdefault]{roboto}

\setlength\parindent{0pt}

% --- Hyperlinks ---
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=darkblue,
}

% --- Section Formatting ---
\titleformat{\section}
  {\large\bfseries\color{darkblue}}
  {}
  {0em}
  {}
  [\titlerule]
\titlespacing*{\section}{0pt}{0.3cm}{0.2cm}

\titleformat{\subsection}
  {\bfseries\color{black}}
  {}
  {0em}
  {}
\titlespacing*{\subsection}{0pt}{0.1cm}{0.05cm}

% --- Custom Commands ---
\newcommand{\entry}[4]{
    \textbf{#1} \hfill #2 \\
    \textit{#3} \hfill \textit{#4} \\
}

\newcommand{\resitem}[1]{\item \small #1}

\begin{document}

% --- Header ---
\begin{flushleft}
    {\Huge \textbf{Ruben IFRAH}} \\ [0.1cm]
    {\Large M.Sc. Student in AI (IASD) -- École Polytechnique \& Dauphine-PSL} \\ [0.2cm]
    
    \small
    \faEnvelope \ \href{mailto:ruben.ifrah@polytechnique.edu}{ruben.ifrah@polytechnique.edu} \quad
    \faGlobe \ \href{https://rubenifrah.github.io}{rubenifrah.github.io} \quad
    \faGithub \ \href{https://github.com/rubenifrah}{rubenifrah} \quad
    \faLinkedin \ \href{https://linkedin.com/in/ruben-ifrah-245496253/}{ruben-ifrah} \quad
    \faMapMarker \ Paris, France
\end{flushleft}

\vspace{0.3cm}

% --- Main Content ---
\columnratio{0.55} 
\setlength{\columnsep}{1cm}

\begin{paracol}{2}

    % ---------------- LEFT COLUMN ----------------
    \section*{Education}
    
    \hspace{0.2cm}\entry{Dauphine - PSL}{2025 -- Present}{M2 IASD (AI, Systems, Data)}{Paris, France}
    \vspace{-0.4cm}
    \begin{itemize}[leftmargin=*, noitemsep]
        \resitem{Highly selective research-oriented Master's program}
        \resitem{Directed by Olivier Cappé \& Francis Bach}
        \resitem{co-accredited ENS-Ulm \& Mines Paris}
    \end{itemize}
    
    \vspace{0.2cm}
    
    \hspace{0.2cm}\entry{École Polytechnique}{2021 -- 2025}{Ingénieur Polytechnicien diploma}{Palaiseau, France}
    \vspace{-0.4cm}
    \begin{itemize}[leftmargin=*, noitemsep]
        \resitem{Majored in Applied Maths and Statistics}
        \resitem{Economy minor: econometrics, financial models, micro/macro economy}
        \resitem{Strong scientific background: general physics, quantum physics, fluid mechanics, solid mechanics, econo-physics}
        \resitem{GPA: 3.7/4.0}
    \end{itemize}
    
    \vspace{0.2cm}
    
    \hspace{0.2cm}\entry{Lycée Saint-Louis}{2019 -- 2021}{CPGE PCSI-PSI*}{Paris, France}
    \vspace{-0.4cm}
    \begin{itemize}[leftmargin=*, noitemsep]
        \resitem{A two-year intensive program in physics, mathematics and engineering sciences}
        \resitem{Top of the 2020-2021 PSI* class}
    \end{itemize}


    \section*{Experience}
    
    \hspace{0.2cm}\entry{Clevaligner}{June 2025 -- Aug. 2025}{Data Scientist Intern}{Paris, France}
    \vspace{-0.4cm}
    \begin{itemize}[leftmargin=*, noitemsep]
        \resitem{Worked in a startup on AI applied to the medical field (dental correction).}
        \resitem{Responsible for assessing and implementing SOTA models in point-cloud teeth segmentation (Transformer-based PointNet).}
        \resitem{Assisted AI engineers in designing and constructing point-cloud pipelines.}
    \end{itemize}

    \vspace{0.2cm}

    \hspace{0.2cm}\entry{University of Valencia}{April 2024 -- July 2024}{Research Assistant (Statistics)}{Valencia, Spain}
    \vspace{-0.4cm}
    \begin{itemize}[leftmargin=*, noitemsep]
        \resitem{Worked on ecological inference estimators and statistical modeling.}
        \resitem{Developed an extended model using different norms for estimator efficiency.}
    \end{itemize}

    \vspace{0.2cm}

    \hspace{0.2cm}\entry{MBDA}{May 2023 -- Aug. 2023}{Applied Research Intern}{Plessis-Robinson, France}
    \vspace{-0.4cm}
    \begin{itemize}[leftmargin=*, noitemsep]
        \resitem{Conducted applied research to optimize anti-jamming filters on stochastic signals.}
        \resitem{Developed advanced stochastic models and simulations using MATLAB.}
        \resitem{Collaborated with defense industry experts on signal processing challenges.}
    \end{itemize}

    \vspace{0.2cm}
    
    \hspace{0.2cm}\entry{French Army (Saint-Cyr)}{Sept. 2021 -- April 2022}{Officer Cadet / Platoon Leader}{Martinique \& Coëtquidan}
    \vspace{-0.4cm}
    \begin{itemize}[leftmargin=*, noitemsep]
        \resitem{\textbf{Platoon Leader (Jan 2022 - April 2022):} Led a platoon of 30 new recruits soldiers in Martinique. Organized training exercises and managed logistics.}
        \resitem{\textbf{Military Academy (Sept 2021 - Jan 2022):} Intensive officer training at Saint-Cyr Coëtquidan. Developed leadership, rigor, and team management skills.}
    \end{itemize}

    \switchcolumn
    
    % ---------------- RIGHT COLUMN ----------------
    
    \section*{Objective}
    \small
    I am an \textbf{Ingénieur Polytechnicien} (X21) currently pursuing the \textbf{M2 IASD} (AI, Systems, Data) at Dauphine-PSL. With a pluridisciplinary background in Physics / Economics and \textbf{Applied Mathematics}, I am looking forward for opportunities in Machine Learning, with a strong interest on Deep-RL and Computer Vision.

    \section*{Personal Projects}
    
    \hspace{0.2cm}\textbf{Deep RL Autonomous Racing Agent} \hfill \href{https://github.com/rubenifrah/spotify-recommender}{GitHub} 
    \begin{itemize}[leftmargin=*, noitemsep]
        \resitem{Developed an autonomous F1 racing agent using PPO, DQN, and Dueling DDQN algorithms.}
        \resitem{Built a custom Gym environment with LIDAR perception and procedural track generation (Harmonic Noise).}
    \end{itemize}

    \vspace{0.2cm}

    \hspace{0.2cm}\textbf{Spotify Recommender System} \hfill \href{https://github.com/rubenifrah/deep-rl}{GitHub} 
    \begin{itemize}[leftmargin=*, noitemsep]
        \resitem{Developed a personal music recommendation pipeline using XGBoost based on my own Spotify playlists}
        \resitem{Implemented custom data balancing strategies (oversampling/undersampling) to handle class imbalance.}
    \end{itemize}

    \section*{Skills}
    \hspace{0.2cm}\textbf{Languages \& Tools}
    \begin{itemize}[leftmargin=*, noitemsep]
        \resitem{Python: Pytorch, Tensorflow, pandas, APIs}
        \resitem{MATLAB, Java, R}
        \resitem{Git, Docker}
    \end{itemize}
    
    \vspace{0.1cm}
    
    \hspace{0.2cm}\textbf{Maths Expertise}
    \begin{itemize}[leftmargin=*, noitemsep]
        \resitem{Stochastic models: Markov Processes, Time series}
        \resitem{Optimization: convex and non-convex}
        \resitem{Numerical Analysis, ODEs}
    \end{itemize}
    
    \vspace{0.1cm}
    
    \hspace{0.2cm}\textbf{Languages}
    \begin{itemize}[leftmargin=*, noitemsep]
        \resitem{\textbf{French:} Native}
        \resitem{\textbf{English:} Advanced (C1)}
        \resitem{\textbf{Spanish:} Working knowledge (B1)}
    \end{itemize}

    \section*{Coursework}
    \hspace{0.2cm}\textbf{AI \& Theory}
    \begin{itemize}[leftmargin=*, noitemsep]
        \resitem{Foundations of Machine Learning (\href{https://scholar.google.com/citations?user=6PJWcFEAAAAJ&hl=fr}{\textit{F. Bach}})}
        \resitem{Reinforcement Learning (\href{https://scholar.google.com/citations?user=erIXTCsAAAAJ&hl=fr}{\textit{O. Cappé}})}
        \resitem{Computer Vision (\href{https://curie.fr/personne/thomas-walter}{\textit{T. Walter}})}
        \resitem{Large Language Models (\href{https://lamsade.dauphine.fr/~allauzen/}{\textit{A. Allauzen}})}
        \resitem{Optimization for Machine Learning (\href{https://www.lamsade.dauphine.fr/~croyer/teach.html}{\textit{C. Royer}})}
    \end{itemize}
    \begin{minipage}[t]{0.2\textwidth}
        \hspace{0.2cm}\textbf{Probability \& Statistics}
        \begin{itemize}[leftmargin=*, noitemsep]
            \resitem{Markov Processes}
            \resitem{Times series}
            \resitem{Probability theory and Stochastic Processes}
        \end{itemize}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.2\textwidth}
        \hspace{0.2cm}\textbf{Databases \& Coding}
        \begin{itemize}[leftmargin=*, noitemsep]
            \resitem{DataBases Management Systems}
            \resitem{Data acquisition}
            \resitem{Python for ML}
        \end{itemize}
    \end{minipage}
    
    \vspace{0.2cm}
    \hspace{0.2cm}\textbf{Other science courses}
    \begin{itemize}[leftmargin=*, noitemsep]
            \resitem{\textbf{Physics}: Quantum Physics, General Physics, \\Electromagnetism}
            \resitem{\textbf{Mechanics}: Fluid Mechanics, Solid Mechanics}
            \resitem{\textbf{Economy}: Econo-Physics, Econometrics, Micro/Macro-economy}
        \end{itemize}
    
    \vspace{0.1cm}
    

\end{paracol}
\end{document}